Semi-Permeable Vesicles: Mathematical Formulation, Numerics, and Physics

### 2020-08-20 vesicle_code/docs/permeableVes/main.tex
adding new image to pnas draft

\newif\ifTikz
%\Tikztrue
\Tikzfalse

@@

\todo[inline]{redo this paragraph}
Finally, letting $\beta=1$, we consider a semi-permeable vesicle that
initially has regions of positive and negative curvature. The vesicle
tension, $\Lambda$, and the flux, $\ff \cdot \nn$,
are plotted in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes
three general behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the
vesicle has a net negative flux resulting in a loss of area; (ii) For $t
\in (1.6 \times 10^{-2},1.0)$, the vesicle has a net positive flux and
the tension most of the membrane is undergoing negative tension; (iii)
For $t \in (1.0,2.0)$, the vesicle is near its steady state and
transitions to a positive constant tension. In the first time interval,
the vesicle deflates. Near the points of largest negative curvature,
there is a large negative tension and large inflow (positive flux).
Correspondingly, near the points with largest positive curvature, there
is a small tension and outflow (negative flux). In the second time
interval, the tension is negative and the flux is positive nearly
everywhere. The regions with largest negative curvature correspond to
regions with largest negative tension and the most inflow. Finally, in
the last time interval, the tension transitions to a positive constant
function, the membrane force and flux transition to zero, resulting in a
steady state circular vesicle with positive constant tension.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}

  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
  flux (bottom) of the semi-permeable vesicle in a quiescent
  flow with $\beta=1$.}
\end{figure}

@@

>>>>

\newif\ifTikz
\Tikztrue
%\Tikzfalse

@@

We next investigate the interplay between the tension, flux, and
curvature of a semi-permeable vesicle. We let $\beta = 1$ and initialize
the vesicle with regions of both positive and negative curvature. The
vesicle tension, $\Lambda$, and the flux, $\ff \cdot \nn$, are plotted
in Figure~\ref{fig:starTensionFlux}. The vesicle undergoes three general
behaviors: (i) For $t \in (0,1.6 \times 10^{-2})$, the vesicle has a net
negative flux resulting in a loss of area; (ii) For $t \in (1.6 \times
10^{-2},1.0)$, the vesicle has a net positive flux and the tension along
most of the membrane is negative; (iii) For $t \in (1.0,2.0)$, the
vesicle is near its steady state and transitions to a positive constant
tension. In the first time interval, the vesicle deflates. Near the
points of largest negative curvature, there is a large negative tension
and large inflow (positive flux).  Correspondingly, near the points with
largest positive curvature, there is a small tension and outflow
(negative flux). In the second time interval, the tension is negative
and the flux is positive nearly everywhere. The regions with largest
negative curvature correspond to regions with largest negative tension
and the most inflow. Finally, in the last time interval, the tension
transitions to a positive constant function, the membrane force and flux
transition to zero, resulting in a steady state circular vesicle with
positive constant tension.

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}

  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}

  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}

  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}

  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime5.pdf}
  \includegraphics[width=0.48\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
  \caption{\label{fig:starTensionFlux} The vesicle tension (left) and
  flux (right) of the semi-permeable vesicle in a quiescent flow with
  $\beta=1$.}
\end{figure}

%\begin{figure}[htp]
%  \centering
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime1.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime2.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime3.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarTensionTime4.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm,clip=true]{figures/StarTensionTime5.pdf}
%
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime1.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime2.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime3.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime4.pdf}
%  \includegraphics[width=0.18\linewidth,trim =2cm 5cm 0cm 5cm, clip=true]{figures/StarFluxTime5.pdf}
%  \caption{\label{fig:starTensionFlux} The vesicle tension (top) and
%  flux (bottom) of the semi-permeable vesicle in a quiescent
%  flow with $\beta=1$.}
%\end{figure}

@@

\begin{figure}[htp]
  \ifTikz
  \input{figures/parabolicOffCenterPhaseSemipermeable.tikz}
  \fi
%  \caption{\label{fig:parabolicOffCenterPhaseDiagram} Phase diagram of
%  an impermeable vesicle with several different flow rates $U$ and
%  reduced areas $\nu$. As shown by Kaoui et al.~\cite{kao-bir-mis2009},
%  the final vesicle shape is either an axisymmetric parachute or bullet
%  (pink region) or an asymmetric slipper (yellow region).}
\end{figure}
